Multiple imputation of incomplete multilevel data using Heckman selection models

### 2022-11-15 1.Paper/Paper.Rmd
update

---
title: Multiple imputation of incomplete multilevel data using Heckman selection models
author:
- name: Johanna Munoz*
  num: a
- name: Valentijn M. T. de Jong
  num: a,b
- name: Thomas. P. A. Debray
  num: a,c
address:
- num: a
  org: Julius Center for Health Sciences and Primary Care, University Medical Center Utrecht, Utrecht University, Utrecht, The Netherlands
- num: b
  org: Data Analytics and Methods Task Force, European Medicines Agency, Amsterdam, The Netherlands
- num: c
  org: Smart Data Analysis and Statistics, Utrecht, The Netherlands

>>>>

---
title: Multiple imputation of incomplete multilevel data using Heckman selection models
author:
- name: Johanna Munoz*
  num: a
- name: Matthias Egger 
  num: d  
- name: Orestis Efthimiou
  num: d
- name: Valentijn M. T. de Jong
  num: a,b,e
- name: Thomas. P. A. Debray
  num: a,c,e
address:
- num: a
  org: Julius Center for Health Sciences and Primary Care, University Medical Center Utrecht, Utrecht University, Utrecht, The Netherlands
- num: b
  org: Data Analytics and Methods Task Force, European Medicines Agency, Amsterdam, The Netherlands
- num: c
  org: Smart Data Analysis and Statistics, Utrecht, The Netherlands 
- num: d
  org: University of Bern, Switzerland
- num: e
  org: These authors contributed equally
